Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2021-11-15 sports_analytics.Rmd
I had to use reticulate.

```{r chess-startup, fig.cap="The starting chess board printed via the \\pkg{chess} package."}
library(chess)
game() %>%
  plot()
```

>>>>

```{r chess-startup, fig.cap="The starting chess board printed via the \\pkg{chess} package."}
library(chess)
Sys.setenv(RETICULATE_PYTHON = "my_env/bin/python")
game() %>% plot()
```
